Clustering based on probability distributions with application on residential customers

### 2021-10-18 main.Rmd
added pre-processing steps

    **Data transformation:** Both robust scaling method and NQT are used before computing the JS-based distances and NQT is built-in transformation used for computation of $wpd$, which forms the basis of wpd-based distances.

    Robust scaling would keep the distribution intact

Normal-Quantile transform will transform the positively and negatively skewed distribution to a similar bell-shaped. From the transformed distribution, it is difficult to understand that raw distribution was of which shape. Also, multimodality gets hidden or magnitude get reversed with NQT. But deciles from the distribution will move in a similar manner as the raw distribution and hence the final distance matrix seem to be unaffected. Hence, this could be used. Also, practically most problems will have a very skewed distribution, it is often helpful to bring them to a normal-like shape before clustering.

>>>>

Practically most problems will have a very skewed distribution, it is often helpful to bring them to a normal-like shape before clustering. Two data transformation techniques are employed for the JS-based methods and NQT is built-in transformation used for computation of $wpd$, which forms the basis of wpd-based distances.

_Robust scaling_ Standardizing is a common scaling method that subtracts the mean from values and divides by the standard deviation, resulting in a conventional Gaussian probability distribution for an input variable (zero mean and unit variance). If the input variable includes outlier values, standardisation may become skewed or prejudiced. To address this, robust scaling methods could be utilized  (value – median) / (p75 – p25)) which results in a variable with a zero mean and median, as well as a standard deviation of one, while the outliers are still there with the same relative connections to other values.

_Normal-Quantile transform_  First as a data pre-processing step to make all assymetrical real world variables more symmetric, we perform a quantile-normal transform on the data. This makes sure that the CDF of the resulting variable in Gaussian. The original data is ranked in ascending order and the probabilities $P(Y<=y(i)) = i/(n+1)$ are attached to $y(i)$, in terms of their ranking order. A NQT based transformation is applied by computing from a standard normal distribution a variable $\eta(i)$, which corresponds to the same probability $P(\eta< \eta(i)) = i/n+1$. By doing this, the new variables $\eta(i)$ will be marginally distributed according to standard Normal, N(0,1). NQT will transform the positively and negatively skewed distribution to a similar bell-shaped. From the transformed distribution, it is difficult to understand that raw distribution was of which shape. Also, multimodality gets hidden or magnitude get reversed with NQT. But deciles from the distribution will move in a similar manner as the raw distribution and hence the final distance matrix seem to be unaffected. Hence, this could be used.
